---
title: How can we increase our confidence in our results.
author: Jake Bowers
date: '`r format(Sys.Date(), "%B %d, %Y")`'
mainfont: "Minion Pro"
output:
  beamer_presentation:
    latex_engine: xelatex
    template: sbst.beamer
    keep_tex: yes
    toc: yes 
  pdf:
    toc: yes
---


```{r include=FALSE, cache=FALSE}
## the toc: yes line above tricks pandoc into running latex twice so that we can see the nice logos

# Some customization.  You can alter or delete as desired (if you know what you are doing).
# knitr settings to control how R chunks work.

require(knitr)
opts_chunk$set(
	       tidy=FALSE,     # display code as typed
	       size="footnotesize",    # slightly smaller font for code
	       echo=TRUE,
	       results='markup',
	       strip.white=TRUE,
	       cache=FALSE,
	       highlight=TRUE,
	       width.cutoff=132,
	       size='footnotesize',
	       out.width='.9\\textwidth',
	       message=FALSE,
	       comment=NA)
```

# What is this about?

The report is coming.

We want to have confidence in our results.

How shall we do this?

# High level process

A second pair of eyes.

Different levels of scrutiny depend on divergence from priors: can you re-run my code? can you re-create my results (numbers, figures, tables) without seeing my code?



# Nitty Gritty 

What does a second pair of eyes imply?

Assume a colleague will need to re-run all of your code.

# Best Practices to Have a Good Relationship With Colleagues (including your future self)}

# How to share data?

**General Idea:** Everyone work with the same original data. If possible, keep data remote.

# Google Sheets

For example, some data can be stored in our Google Drive:

```{r}
## The first time this is run in a while, you'll need to run each line by hand. Thereafter, it should all work smoothly.
library(googlesheets)
countyCountsGS<-gs_title("countyCountsFIPS.csv") ## get info about the data
countyCounts<-as.data.frame(gs_read_csv(countyCountsGS,as.is=TRUE),stringsAsFactors=FALSE)
str(countyCounts)
```
# Data Online

Other data can be read directly from a website:
```{r}
usaCountiesPopCentroids<-read.csv(url("http://www2.census.gov/geo/docs/reference/cenpop2010/county/CenPop2010_Mean_CO.txt"),as.is=TRUE)
head(usaCountiesPopCentroids)
```

# Small Data on Github

# Plain Text Data If Possible 



